---
title: "HW1"
format: html
editor: visual
---

## What do you think being a data scientist is about?

Data science is a discipline that allows you to take raw data from many different situations and transform that data into communicable knowledge.

## What differences/similarities do you see between data scientists and statisticians?

Data scientists study structured data. Statisticians use mathematical and statistical methods to collect and interpret data. These careers are similar in their need for expertise in statistical analysis, knowledge of programming languages, and mathematical knowledge. They differ in their scope. Data science is new, and highly interdisciplinary. Statistics is much older, and while statisticians use technology they are also more likely to use mathematical concepts in their work. Data scientists are also high in demand in industry, where statisticians are more likely to be employed in academic, government or research positions. There are also differences in the focus of their work and tools they use to complete it.

## How do you view yourself in relation to these two areas?

I identify more as a mathematician than data scientist or statistician. However, I also love statistics, and the evolving nature of data science has made me interested in learning more about it.

## Load the Dataset

Here we load the `iris` data set, which contains measurements of flowers.

```{r}
y <- density(iris$Petal.Width)
```

## Summarize the Data

Now we compute summary statistics to see the overall structure of the data set.

```{r}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)

```

## Plot of Data

Here we plot the `iris` data set.

```{r, echo=FALSE}
y <- density(iris$Petal.Width)
plot(y)

```
